On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-15 manuscripts/PNAS/review/point_by_point_response.txt

-----------------
Since the result is an extension of the noise-free result of [HS15] to a noisy case, the authors should provide better justification for the significance of contributions. The main result seems to be based on an approach similar to [HS15], and there is little to no discussion of the computability and tightness of the sufficient condition for stability in the main results. Thus, the submission does not seem to be greatly more valuable than [HS15] and also not conclusive regarding the central problems of sparse linear coding and dictionary learning. That being said, the paper (with the modifications below) would certainly merit publication in very solid journal like IEEE Transactions on Information Theory, where it would be a median paper, in my opinion.
-----------------

RESPONSE:

We agree with the reviewer that a straightforward extension of the approach and noise-free result of [HS15] to the noisy case — while still a significant advancement in applied mathematics with actual practical implications — would not necessarily merit publication in PNAS on its own. The reviewer, however, seems to have overlooked the fact that our main result (Thm. 1) generalizes the noise-free result of [HS15] far beyond a simple extension to the noisy case in ways which provide valuable insight into the dictionary learning model and that a significant deviation from the approach taken in [HS15] was necessary to prove these new facts. Moreover, our solution (Cor. 2) to the optimization formulation of the dictionary learning problem (Prob. 2) — that of most interest to optimization theorists and practitioners of their methods — is (to our knowledge) the first of its kind in both the noise-free and noisy domains. We discuss all of these points in more detail in our response to the reviewer’s later "detailed comments".

We have included in our updated manuscript a discussion of the computability of the sufficient conditions (they are, indeed, computable), as per the reviewer’s request. The main constants in our work -- C_1, C_2 -- are computable, elementarily, in terms of two positive quantities that are natural in our context: (a) the "Lower Bound" L_H(A) of a matrix A given a hypergraph H (the support sets of sparse x's generating the data — see *NOTE* below this paragraph), which is a measure of how distinguishable two x’s with supports in H are by their images under A, and (b) the value in Def. 4 of r(V_1,...,V_l) given subspaces V_i spanned by columns of A, which bounds the distance between intersections of such subspaces and each subspace individually. The first quantity (a) is, in some form or another, related to standard objects in the field and may be computed as the smallest singular value of a set of specific sub-matrices; in particular, for fixed sparsity constraint k on H, the lower bound L_H(A) is efficiently computable (polynomial time). Because deciding L_H(A) > 0 is already NP-hard [TP14], it seems likely that without fixing a sparsity level there is no efficient computation in general for (a). The calculation of (b) involves determining "canonical angles" between subspaces, which is usually reduced again to a numerical (efficient) singular value decomposition given the fixed subspaces.  However, upon close inspection, C_2 nonetheless requires an exponential number of instances of computing r. Thus, while our constants are effective (an algorithm exists to compute them), they are not necessarily polynomially-time computable.

*NOTE* We have introduced for reasons discussed below the notion of L_H(A) in our re-submission where previously (in our original submission) we had defined only L_k(A).

@@

-- The paper does a good job of motivating the general problem of sparse coding to a general audience. In particular, there is a good review of the areas in which dictionary learning arises.

-- I think the biggest potential issue for publication in PNAS is that the significance of the result needs more discussion. Specifically, the authors could address why going from the noise-free case to the noisy case is not incremental. PNAS specifically targets submissions that go beyond what could be published in a more specialized journal. Could the authors, for example, contrast the proof technique between the noisy and noise-free cases? Or, perhaps, the practical implications?
-----------------

RESPONSE:

With all due respect to the reviewer, we believe the most compelling practical implication of a noisy result over a noiseless result is plainly evident: never has there been an experiment without noise and an unstable model is therefore useless in practice. We assume the reviewer must instead be concerned with what additional practical “take-away” message our manuscript contains.  One significant one is the outline of a procedure which can affirm if one’s proposed solution to Prob. 1 or Prob. 2 is indeed unique. We have updated the manuscript with an explicit statement of this fact, and outline one such procedure here:

@@

Given a dictionary A and codes x_i that solve Problem 1 (e.g. learned by any algorithm), check that that they satisfy the assumptions of Thm. 1:
   - List the support sets of the x_i 
      - Discard those for which there are (k-1){m \choose k} or fewer x_i with that support.
      - Discard those for which the supported x_i are not in GLP. (This should also exclude any supports less than k in size.)
   - From the support sets that remain, list all SIP-satisfying hypergraphs that are subsets of this set
   - Discard those for which L_{2H}(A) = 0.
   - For each of the remaining hypergraphs, determine the constant C_1 from A and the x_i (or for every subset of the x_i of size (k-1){m \choose k})
   - Check that the derived upper bound on \varepsilon exceeds that of the original problem. If yes, the solution is “unique”.

More practical implications arise from our discovery of sufficient combinatorial designs for support sets of generating codes x_i, which have implications for polynomial time. Moreover, we have shown that a subset of dictionary elements are recoverable even if the number of dictionary elements in total is unknown; these observations are discussed in more detail below.

@@

To be clear, the new perspective we take on the problem yields the following powerful conclusions beyond those of a straightforward extension of [HS15] to the noisy case:

1) An extension to the case where the number of dictionary elements is unknown: The results of [HS15] only apply to the case where the matrix B has the same number of columns as A. We forgo this assumption and show that B must have at least as many columns as A and contains (up to noise) a subset of the columns of A. The size of this subset depends on a simple relation between the number of columns of B and the regularity of the support-set hypergraph.

2) A significant reduction in sample complexity: To identify the n x m generating dictionary A, [HS15] require that data be sampled from every k-dimensional subspace spanned by the m columns of A (that is, {m \choose k} subspaces in total). We show that the data need only be sampled from m subspaces in total (e.g. those supported by consecutive intervals of length k in some cyclic order on [m]) and in some cases as few as 2\sqrt{m} (e.g. when m = k^2, take the supports to be the rows and columns of [m] arranged in a square grid). Moreover, if the size of the support set of reconstructing codes is known to be polynomial in m and k, then the pigeonholing argument in the proof of Thm. 1 requires only a polynomial number of samples distributed over a polynomial number of supports; thus, N is polynomial in m, k. This point was only hinted at in the Discussion section of our original submission, but we have included it in the updated manuscript to make clear the power of our approach over that taken in [HS15]. We are aware of only one work treating combinatorial hypergraph designs in the setting of dictionary learning, "An incidence geometry approach to dictionary learning" (arxiv, non-published paper)

@@

RESPONSE: Yes, thanks for this question. The condition on \ell is perhaps best understood as a condition on \bar m not being too large (given \ell) in order to guarantee the recovery of at least one dictionary element. We have updated the manuscript to reflect this, and the condition now reads “provided \bar m < \ell m / (\ell - 1)” where previously it read “provided p = \bar m − \ell( \bar m − m ) is positive”.

-----------------
-- The paper could also compare the sample complexity results on N with those given in the noise-free case. For example, Table I in reference (18) gives a comparison of sample complexity requirements for different conditions in the noise-free case. Where would the results of this paper stand in that table?

-- Otherwise, all the math seemed correct.
-----------------

RESPONSE: We appreciate this question but, since in all comparable cases the sample complexities improve in this work, we feel that an explicit comparison would not be the best use of our limited space; although we are willing to do so if necessary. Many thanks for your careful review of the mathematics. We have tried and continue to try to be as clear, concise, and correct as we possibly can to elevate this work into the top echelon of applied mathematical theory papers.

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
crafty edits

Another practical implication of this result is the following: there is an effective procedure by which one can affirm if one's proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities). One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.  
%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.

@@

We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data. As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order. Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}. %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
This weakening of condition \eqref{SparkCondition} allows for a practical amount of data (polynomial-time for fixed sparsity $k$) for guaranteeing stable sparse representation.

There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.  For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to data.

\begin{theorem}\label{SLCopt}
If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy implications \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
\end{theorem}

@@

Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$, in fact, form a set of measure zero. Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero). Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.

@@

We remark that these results have a strong application to theoretical neuroscience, mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.

@@

The heart of the matter is therefore \eqref{Cstable}, which we now finally establish, first in the important special case $k = 1$

@@

It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$. Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$. Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\bar S}$}, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\bar{X}}_K)_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef} we have:
\begin{align}\label{rhs222}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S}) 
\leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
\end{align}
%
where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
\end{proof}

@@

[*** ADD:  Ganguli, Deep Learning, constants, tightness, ***]

@@

\begin{lemma}\label{NonEmptyLemma}
Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap h(i)| = 1$ for all $i \leq q$. Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
\begin{align}\label{pcond}
\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p.
\end{align}

If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} (|\pi(S)| -|S|) \geq 0$ and:
\begin{align}\label{cond}
|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} | \text{ for all } \mathcal{G} \subseteq \mathcal{H},
\end{align}
then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some nonempty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$. In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$. 
\end{lemma}

@@

We next show that \eqref{cond} holds.  Fix $\mathcal{G} \subseteq \mathcal{H}$. Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in \mathcal{G}} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true. Suppose then that the intersection is not the zero vector. Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound} and finally \eqref{Cdef2} gives:
\begin{align}\label{randoml}
d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}&, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
\leq d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in \mathcal{G}} \bm{\mathcal{A}}_S \right) \nonumber \\
&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
&\leq \frac{|\mathcal{G}| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
\leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
\end{align}

Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is strictly less than one. Hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.

@@

\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$. % for space:  (e.g.,  \cite{folland2013real}). 
By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds with probability one.
\end{proof}

>>>>

Another practical implication of Thm.\ref{DeterministicUniquenessTheorem} is the following: there is an effective procedure sufficient to affirm if a proposed solution $(\mathbf{B}, \mathbf{\bar x}_1, \ldots, \mathbf{x}_N)$ to Prob.~\ref{InverseProblem} is indeed unique (up to noise and inherent ambiguities). One simply checks that $\mathbf{B}$ and the $\mathbf{\bar x}_i$ satisfy the respective assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.  
%. on $\mathbf{A}$ and the $\mathbf{x}_i$, respectively.

@@

We furthermore note that unlike the requirements of previous works \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}, the matrix $\mathbf{A}$ need not satisfy the spark condition to be recoverable from data. As a simple example for $k=2$, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ where $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$, and take $\mathcal{H}$ to be all consecutive pairs of $[m]$ arranged in cyclic order. Then, $\mathbf{A}$ satisfies the assumptions of Thm.~\ref{DeterministicUniquenessTheorem} but not \eqref{SparkCondition}. %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
This weakening allows for a practical amount of data (polynomial-time for fixed sparsity $k$)  guaranteeing stable dictionaries.

There are other less direct consequences of Thm.~\ref{DeterministicUniquenessTheorem}.  For instance, we use it to prove uniqueness for the optimization formulation of dictionary learning, Prob.~\ref{SLCopt}, the main object of interest for those applying dictionary learning to their data.

\begin{theorem}\label{SLCopt}
If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold, only now with more than $(k-1)\left[ {\bar m \choose k} + |\mathcal{H}|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported in each $S \in \mathcal{H}$, then all solutions to Prob.~\ref{OptimizationProblem} necessarily satisfy recovery inequalities \eqref{Cstable} and \eqref{b-PDa} of Thm.~\ref{DeterministicUniquenessTheorem}.
\end{theorem}

@@

Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero. Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero). Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.

@@

We remark that these results have a surprising application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10}.

@@

The heart of the matter is therefore \eqref{Cstable}, which we now establish, first in the important special case $k = 1$

@@

It follows from $L_{2\mathcal{H}}(\mathbf{A}) > 0$ and the general linear position of the $\mathbf{x}_i$ that $L(\mathbf{AX}_{K}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\bm{\mathcal{A}}_S$. Fixing $\mathbf{0} \neq \mathbf{y} \in \bm{\mathcal{A}}_S$, there then exists $\mathbf{0} \neq \mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$. Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \bm{\mathcal{B}}_{\bar S}$}, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\bar{X}}_K)_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef}:
\begin{align}\label{rhs222}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\bar S}) 
\leq \frac{\varepsilon}{  L(\mathbf{AX}_{K}) } \leq \varepsilon \frac{C_1}{C_2},
\end{align}
%
where the second inequality is due to $L(\mathbf{AX}_{K}) \geq L_k(\mathbf{AX}_{I(S)})$ and \eqref{Cdef1}. Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$.
\end{proof}

@@

@@

\begin{lemma}\label{NonEmptyLemma}
Fix a hypergraph $\mathcal{H} \subseteq 2^{[m]}$ with nodes labeled in order of non-increasing degree and for which $|\cap h(i)| = 1$ for all $i \leq q$. Fix $\bar m$ and let $p \leq q$ be the largest number satisfying:
\begin{align}\label{pcond}
\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p.
\end{align}
If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in \mathcal{H}} (|\pi(S)| -|S|) \geq 0$ and:
\begin{align}\label{cond}
|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} | \text{ for all } \mathcal{G} \subseteq \mathcal{H},
\end{align}
then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(h(i))$ defines an injective map to $[\bar m]$ from some nonempty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$. In particular, if $\mathcal{H}$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$. 
\end{lemma}

@@

We next show that \eqref{cond} holds.  Fix $\mathcal{G} \subseteq \mathcal{H}$. Since $\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})} \subseteq \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}$, if $\cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)} = \{\textbf{0}\}$, then we must have $|\cap_{S \in \mathcal{G}} \pi(S)| = 0$ (as the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent) and \eqref{cond} is trivially true. Suppose then that the intersection is not the zero vector. Keeping in mind that $d(U,V) \leq d(U',V)$ whenever $U \subseteq U'$ and applying (in order) Lem.~\ref{spanIntersectionLemma}, Lem.~\ref{DistanceToIntersectionLemma}, \eqref{eqdim}, \eqref{GapUpperBound}, and \eqref{Cdef2} gives:
\begin{align}\label{randoml}
d(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}&, \bm{\mathcal{A}}_{\cap \mathcal{G}}  ) 
\leq d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)}, \cap_{S \in \mathcal{G}} \bm{\mathcal{A}}_S \right) \nonumber \\
&\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \cap_{S \in \mathcal{G}} \bm{\mathcal{B}}_{\pi(S)},\bm{\mathcal{A}_{T}} \right) }{ r(  \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }
\leq \sum_{T \in \mathcal{G}} \frac{ d\left( \bm{\mathcal{B}}_{\pi(T)},\bm{\mathbf{A}}_{T} \right) }{ r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}}) }\nonumber \\
&\leq \frac{|\mathcal{G}| \varepsilon}{r( \{\bm{\mathcal{A}}_S\}_{S \in \mathcal{G}})} 
\leq \frac{C_2 \varepsilon}{\max_i\|\mathbf{A}_i\|_2}. 
\end{align}

Since $\varepsilon < L_2(\mathbf{A}) / C_2$, by \eqref{delrho} the right-hand side in \eqref{randoml} is less than one. Hence, $\dim(\bm{\mathcal{B}}_{\cap \pi(\mathcal{G})}) \leq \dim(\bm{\mathcal{A}}_{\cap \mathcal{G}})$ by \eqref{dimLem}, and \eqref{cond} follows from the linear independence of the columns of $\mathbf{A}_{S}$ and $\mathbf{B}_{\pi(S)}$ for all $S \in \mathcal{G}$.

@@

\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$. % for space:  (e.g.,  \cite{folland2013real}). 
By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability is almost sure.
\end{proof}
